Cartograms with Rivers

### 2022-11-09 paper/GHRVis.tex
draft: limitations and conclusions

@@

\author[Q. Wang, K. Xu \& R. S. Laramee]
{\parbox{\textwidth}{\centering Q. Wang, K. Xu
  and R. S. Laramee
    }
    \\
\parbox{\textwidth}{\centering School of Computer Science, University of Nottingham, UK}
}

@@

\section{Limitations and Future Work}

\section{Conclusions}

\section{Acknowledgments}
This work is funded by the grant EP/S010238/2 from the Engineering and Physical Sciences Research Council (EPSRC). EPSRC is a British Research Council that provides government funding for grants to undertake research and postgraduate degrees in engineering and the physical sciences.

@@

\cleardoublepage

>>>>

% For cover's captionof
\usepackage[font=normalfont,labelfont=bf]{caption}

@@

\author[Q. Wang, K. Xu \& R. S. Laramee]
{
\parbox{\textwidth}{\centering Q. Wang, K. Xu and R. S. Laramee}
\\
\parbox{\textwidth}{\centering School of Computer Science, University of Nottingham, UK \\ \begin{center}
    \centering
    \includegraphics[height=3cm,keepaspectratio]{figure/cover.png}
    \captionof{figure}{The River Thames passing through NHS Clinical Commissioning Groups in London and surrounding areas.}
\end{center}
}
}

@@

\input{section/limitation}

\input{section/conclusion}

% \section{Acknowledgments}
% This work is funded by the grant EP/S010238/2 from the Engineering and Physical Sciences Research Council (EPSRC). EPSRC is a British Research Council that provides government funding for grants to undertake research and postgraduate degrees in engineering and the physical sciences.

@@

\clearpage

### 2022-11-09 paper/section/evaluation.tex
draft: limitations and conclusions

\color{blue}

\newcommand{\pCount}{14 }
\section{User-Centered Evaluation}

@@

\subsection{User Study}

\subsubsection{Participants}

We recruited \pCount participants, ...

\subsubsection{Datasets}

We used the following datasets for our evaluation:

@@

In this section we analyze the results of our user study. We recruited \pCount participants to perform 16 location tasks.

{
    \begin{figure}[htb!]
        \centering
        \includegraphics[width=\columnwidth,keepaspectratio]{figure/evaluation/task-rt.png}
        \caption{The scatter plot shows the response time (in seconds) and answers for each task, filtering out [add the exact number in the end] responses that took over 20 seconds.}
        \label{fig:task-rt}
    \end{figure}
}

\color{black}

>>>>

\newcommand{\pCount}{15 }
\section{User-Centered Evaluation}

@@

\subsection{User Study}
In this section we describe the user study participants, datasets, and the experiment procedure.

\bobgraph{Participants:} We recruited \pCount participants.

\begin{itemize}
    \item Gender:  8 females and 7 males
    \item Age Group:   18-24 (7), 25-29 (8)
    \item Education:   3 Bachelor's, 11 Master's, 1 PhD
\end{itemize}

\bobgraph{Datasets:} We used the following datasets for our evaluation:

@@

In this section we analyze the results of our user study. We recruited \pCount participants to perform 16 location tasks each, in total we collected 240 responses, 59 responses that took over 20 seconds are excluded from the analysis.

{
    \begin{figure}[htb!]
        \centering
        \includegraphics[width=\columnwidth,keepaspectratio]{figure/evaluation/task-rt.png}
        \caption{The scatter plot shows the response time (in seconds) and answers for each task. Correct answers are shown in green circle, and incorrect answers are shown in red triangle. Solid glyphs represent the task without rivers, and hollow glyphs represent the task with rivers.}
        \label{fig:task-all}
    \end{figure}
}

\bobgraph{Accuracy:} \Cref{fig:task-acc} shows the accuracy measured by the number of correct CCGs chosen by the participants. The chart shows that the introduction of rivers has improved the accuracy for two CCGs. The accuracy for the two groups differs significantly according to the two-sample unequal variance $t$-test performed, $t$(176.43) = 2.92, $p$ = 0.0039. This supports our hypothesis H1 that the introduction of rivers improves the legibility of cartogram.

{
    \begin{figure}[htb!]
        \centering
        \includegraphics[width=\columnwidth,keepaspectratio]{figure/evaluation/accuracy.png}
        \caption{The bar chart shows the accuracy of locating CCGs.}
        \label{fig:task-acc}
    \end{figure}
}

\bobgraph{Response Time:} \Cref{fig:task-rt} shows the average response time measured for four CCGs. The chart shows that the introduction of rivers has slightly reduced the time needed to locate CCGs. The two groups show no significant differences according to the two-sample unequal variance $t$-test performed, $t$(168.03) = 1.29, $p$ = 0.20.  The statistical analysis does not support our hypothesis H2, that the introduction of rivers does not reduce the response time significantly.

{
    \begin{figure}[htb!]
        \centering
        \includegraphics[width=\columnwidth,keepaspectratio]{figure/evaluation/rt.png}
        \caption{The bar chart shows the average response time for locating CCGs.}
        \label{fig:task-rt}
    \end{figure}
}

### 2022-11-09 paper/section/main.tex
draft: limitations and conclusions

\new{The algorithm terminates when the average node size $ \nodeSizeAvg $ reaches the max node size $ \nodeSizeMax $. At this point, the node layout is optimal where no node has crossed, or crossed by a river.}

>>>>

The algorithm terminates when the average node size $ \nodeSizeAvg $ reaches the max node size $ \nodeSizeMax $. At this point, the node layout is optimal where no node has crossed, or crossed by a river.
